Red-Giant Hot Jupiters: Brilliant Radio Beacons? \memoTM{Since they are not that bright, maybe ``The Radio Emission from Red-Giant Hot Jupiters'' or ``A Novel Method for Detecting Red-Giant Hot Jupiters'' would be a better title?}

### 2015-09-09 ms.tex
Switched affiliation order.

\affil{$^2$Astrophysics Department, Institute for Advanced Study,
  Princeton, NJ 08540}

@@

\affil{$^4$Analytics \& Algorithms, Stitch Fix,
  San Francisco, CA  94103}

>>>>

\affil{$^2$Analytics \& Algorithms, Stitch Fix,
  San Francisco, CA  94103}

@@

\affil{$^4$Astrophysics Department, Institute for Advanced Study,
  Princeton, NJ 08540}
